Conservation decision-making under long transients

### 2019-08-13 docs/index.Rmd
try renaming for gh-pages hosting

<img src="solarized_files/figure-html/posteriors-1.png" width="400px">

@@

<img src="solarized_files/figure-html/arima_forecast-1.png" width="100px" height="60px"> Ghost attractors look like real attractor but behave differently

@@

<img src="solarized_files/figure-html/wtf-1.png" width="100px" height="60px"> Stochastic ghosts $\neq$ deterministic ones

@@

<img src="solarized_files/figure-html/posteriors-1.png" width="100px" height="60px"> This makes model inference hard!

@@

<img src="solarized_files/figure-html/learning-1.png" width="100px" height="60px"> Reinforcement learning can help deal with uncertainty

@@

<img src="solarized_files/figure-html/less-learning-1.png" width="100px" height="60px"> Precaution is sometimes better than knowledge

>>>>

<img src="index_files/figure-html/posteriors-1.png" width="400px">

@@

<img src="index_files/figure-html/arima_forecast-1.png" width="100px" height="60px"> Ghost attractors look like real attractor but behave differently

@@

<img src="index_files/figure-html/wtf-1.png" width="100px" height="60px"> Stochastic ghosts $\neq$ deterministic ones

@@

<img src="index_files/figure-html/posteriors-1.png" width="100px" height="60px"> This makes model inference hard!

@@

<img src="index_files/figure-html/learning-1.png" width="100px" height="60px"> Reinforcement learning can help deal with uncertainty

@@

<img src="index_files/figure-html/less-learning-1.png" width="100px" height="60px"> Precaution is sometimes better than knowledge
